---
title: "Workflow"
output: html_document
date: "2023-06-08"
---

```{r, include = FALSE}
knitr::knit_hooks$set(margin = function(before,options,envir) {
if(before) par(mgp=c(1,0.35,0),bty="n",plt=c(0,.99,.13,.99), mar = c(2,2,3,2), xpd = TRUE) else NULL })

knitr::opts_chunk$set(margin=T,prompt=T,comment="",collapse=T,cache=F, bty="n",
dev.args=list(pointsize=11),fig.height= 4,
fig.width=10,fig.retina=2,fig.align="center")
```

## Workflow example

#### Quick checklist summary

1. Setup a repository

    a. create a repository from template
    b. add the configuration files
    c. validate the configuration files
  
  
2. Add Submission files 

3. Load the data

4. Calculate the ensembles

5. Plot the output

##### Library and System setup:

To use full administrator functionality please ensure you install full list of package dependencies including Suggests with:
```{r install, eval=FALSE}
remotes::install_github("Infectious-Disease-Modeling-Hubs/hubUtils",
                        dependencies = TRUE)
remotes::install_github("Infectious-Disease-Modeling-Hubs/hubEnsembles")
```

```{r setup}
library(hubUtils)
library(hubEnsembles)
library(magrittr)
```

#### Setup a repository

See vignette 
["hub-setup"](https://github.com/Infectious-Disease-Modeling-Hubs/hubUtils/blob/main/vignettes/articles/hub-setup.Rmd) 
on 
[hubUtils package](https://github.com/Infectious-Disease-Modeling-Hubs/hubUtils/tree/main)

  
##### Load the submission files

```{r hub_con}
hub_path <- getwd()
hub_con <- connect_hub(hub_path)
hub_con

# Round 1 for example
round1 <- hub_con %>% 
  dplyr::filter(origin_date == as.Date("2021-03-07")) %>% 
  dplyr::collect() %>% 
  dplyr::select(-age_group)
```

##### Calculate ensemble

```{r hub_ens}
# Mean ensemble
round1_ens <- hubEnsembles::simple_ensemble(round1)
head(round1_ens)

## Mean weight ensemble
#weights <- data.frame(
#  "model_id" = c("hubcomp_examp", "HUBuni-simexamp"),
#  "weights" = c(1,0)
#)
#round1_ens <- hubEnsembles::simple_ensemble(round1, weights = weights, 
#                                            weights_col_name = "weights")
#head(round1_ens)
#
## Median ensemble
#round1_ens <- hubEnsembles::simple_ensemble(round1, agg_fun = "median")
#head(round1_ens)
#
## Median weight ensemble
#weights <- data.frame(
#  "model_id" = c("hubcomp_examp", "HUBuni-simexamp"),
#  "weights" = c(1,0)
#)
#round1_ens <- hubEnsembles::simple_ensemble(
#  round1, weights = weights, weights_col_name = "weights", agg_fun = "median")
#head(round1_ens)
#
## Rename output model
#round1_ens <- hubEnsembles::simple_ensemble(
#  round1, agg_fun = "median", model_id = "comp_ensemble")
#head(round1_ens)
#
## Ensemble all scenarios
#col_task_id <- c("origin_date", "location", "target", "horizon")
#round1_ens <- hubEnsembles::simple_ensemble(
#  round1, agg_fun = "median", model_id = "comp_ensemble", 
#  task_id_cols = col_task_id)
#head(round1_ens)
#
## Rename output type id column
#round1_rename <- dplyr::rename(round1, type = output_type, 
#                               type_id = output_type_id)
#round1_ens <- hubEnsembles::simple_ensemble(
#  round1_rename, agg_fun = "median", model_id = "comp_ensemble", 
#  task_id_cols = col_task_id, output_type_col = "type", 
#  output_type_id_col = "type_id")
#head(round1_ens)
#
## Sum ensemble
#round1_ens <- hubEnsembles::simple_ensemble(round1, agg_fun = "sum")
#head(round1_ens)
#
```


#### Plot

```{r plot_setup, message= FALSE}
library(plotly)
```

##### Data processing:

Projection:

```{r plot_process}
plot_round1 <- dplyr::filter(round1, scenario_id == "A-2021-03-05", location == "US", target == "inc case", output_type_id %in% c(0.975, 0.025, 0.5))
plot_round_ens <- hubEnsembles::simple_ensemble(plot_round1, agg_fun = "median")
plot_df <- rbind(plot_round1, plot_round_ens)
plot_df <- dplyr::select(plot_df, origin_date, horizon, output_type_id, value, model_id)
plot_df <- dplyr::mutate(plot_df, target_date = as.Date(origin_date) + (horizon * 7) - 1)
plot_df <- dplyr::select(plot_df, model_id, output_type_id, target_date, value)
head(plot_df)
```

Truth Data:

```{r truth_data_process}
truth_data <- read.csv("target-data/US_inc_case.csv")
truth_data <- dplyr::filter(truth_data, location == "US", time_idx < min(plot_df$target_date))
```

###### Plot: 

```{r plot_function}
# Internal data process for plotting function, returns a list with 2 data frame:
# one for plain lines, one for ribbons plotting
 plot_prep_data <- function(df, plain_line, ribbon) {
    plain_df <- dplyr::filter(df, output_type_id == plain_line) 
    ribbon_df <- dplyr::filter(df, output_type_id %in% ribbon) %>%
      dplyr::mutate(output_type_id = ifelse(output_type_id == min(ribbon), 
                                            "min", "max")) %>% 
      tidyr::pivot_wider(names_from = output_type_id, values_from = value)
    return(list("plain_df" = plain_df, "ribbon_df" = ribbon_df))
}

#' Basic Plot for model outputs
#'
#' Create a simple Plotly time-series plot for model projection outputs. 
#'
#'@param plot_df a `data.frame` object containing the columns: `model_id`, 
#' `output_type_id`, `target_df`, `value`
#'@param truth_df a `data.frame` object containing the ground truth data, 
#' containing the columns: `time_idx` and `value`
#'@param plain_line a `numeric` quantile value, value will be used to create a 
#' plain line in the plot
#'@param ribbon a vector of `numeric` quantile value, value will be used a to 
#' create a ribbon in the plot
#'@param title a `character` string, if not NULL, will be added as title to the 
#' plot
#'@param ens_color a `character` string of a color name, if not NULL, will be 
#' use as color for the model name associated with the parameter `ens_name`
#' (both parameter need to be provided)
#' @param ens_name a `character` string of a model name, if not NULL, will be 
#' use to change the color for the model name, associated with the parameter 
#' `ens_color`(both parameter need to be provided)
basic_plot_function <- function(plot_df, truth_df, plain_line = 0.5, 
                                ribbon = c(0.975, 0.025), title = NULL,
                                ens_color = NULL, ens_name = NULL) {
  
  # Data process
  if (!is.null(ens_color) & !is.null(ens_name)) {
    ens_df <- dplyr::filter(plot_df, model_id == ens_name) 
    all_ens <- plot_prep_data(ens_df, plain_line, ribbon)
    plot_df <- dplyr::filter(plot_df, model_id != ens_name)
  } else {
    all_ens <- NULL
  }
  
  all_plot <- plot_prep_data(plot_df, plain_line, ribbon)
  
  # Plot
  plot_model <- plot_ly(height = 1050, colors = scales::hue_pal()(50)) 
  if (!is.null(truth_df)) {
    plot_model <- plot_model %>% 
      add_trace(data = truth_df, x = ~time_idx, y = ~value, type = "scatter",
                mode = "lines+markers", line = list(color = "#6e6e6e"),
                hoverinfo = "text", name = "ground truth",
                hovertext = paste("Date: ", truth_df$time_value, "<br>", 
                                  "Ground truth: ", 
                                  format(truth_df$value, big.mark = ","), 
                             sep = ""), 
                marker = list(color = "#6e6e6e", size = 7))
  }
  plot_model <- plot_model %>% 
    add_lines(data = all_plot$plain_df, x = ~target_date, y = ~value, 
              color = ~model_id) %>% 
    add_ribbons(data = all_plot$ribbon_df, x = ~target_date, ymin = ~min, 
                ymax = ~max, color = ~model_id, opacity = 0.25, 
                line = list(width = 0), showlegend = FALSE)
  # Ensemble color
  if (!is.null(ens_df)) {
    plot_model <- plot_model %>% 
    add_lines(data = all_ens$plain_df, x = ~target_date, y = ~value, 
              line = list(color = ens_color), color = ~model_id) %>% 
    add_ribbons(data = all_ens$ribbon_df, x = ~target_date, ymin = ~min, 
                ymax = ~max, opacity = 0.25, fillcolor = ens_color,
                line = list(width = 0, color = ens_color), showlegend = FALSE)
  }
  
  # Layout
  plot_model <- plot_model %>% 
    layout(xaxis = list(title = 'Epiweek'), 
           yaxis = list(title = 'Value'))
  if (!is.null(title))
    plot_model <- plot_model %>% layout(title = title)
  
  
}
```

```{r, warning=FALSE}
plot <- basic_plot_function(plot_df, truth_data, 
                            title = "Projected Incident Cases for the US (scenario A; Round 1)",
                            ens_color = "black", ens_name = "hub-ensemble")
plot
```

