---
title: "Workflow Example"
date: "2023-11-14"
---

```{r, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::knit_hooks$set(margin = function(before,options,envir) {
if(before) par(mgp=c(1,0.35,0.1),bty="n",plt=c(0,.90,.13,.90), mar = c(2,2,2,2), xpd = TRUE) else NULL })

knitr::opts_chunk$set(margin = T,prompt = T,comment = "", collapse=F,cache=F, bty="n",
                      dev.args=list(pointsize=11),fig.height= 4,
                      fig.width=10,fig.retina=1,fig.align="center")
```

## Quick checklist summary

1. Setup a repository

    a. create a repository from template
    b. add the configuration files
    c. validate the configuration files
  
  
2. Add Submission files 

3. Load the data

4. Calculate the ensembles

5. Plot the output

## Library and System setup:

To use full administrator functionality please ensure you install full list of package dependencies including Suggests with:
```{r install, eval=FALSE}
remotes::install_github("Infectious-Disease-Modeling-Hubs/hubUtils",
                        dependencies = TRUE)
remotes::install_github("Infectious-Disease-Modeling-Hubs/hubEnsembles")
remotes::install_github("Infectious-Disease-Modeling-Hubs/hubVis")
```

```{r setup, message=FALSE}
library(hubUtils)
library(hubEnsembles)
library(hubVis)

library(dplyr)
```

```{r prerequisite}
# Store the path of the hub
hub_path <- getwd()
```

## Setup a repository

See vignette 
["hub-setup"](https://github.com/Infectious-Disease-Modeling-Hubs/hubUtils/blob/main/vignettes/articles/hub-setup.Rmd) 
on 
[hubUtils package](https://infectious-disease-modeling-hubs.github.io/hubUtils/index.html)

Create the config files: `hub-config/admin.json` and `hub_config/tasks.json` and validate them:

```{r config_valid}
hubUtils::validate_config(hub_path)
hubUtils::validate_config(hub_path, config = "admin")
```
  
or 

```{r}
validate_hub_config(hub_path)
```
  
## Load the submission files

```{r hub_con}
hub_con <- connect_hub(hub_path)
hub_con

# Round 1 for example
round1 <- hub_con %>% 
  dplyr::filter(origin_date == as.Date("2021-03-07")) %>% 
  dplyr::collect()
round1
```

## Calculate ensemble

See 
[hubEnsembles package](https://infectious-disease-modeling-hubs.github.io/hubEnsembles/index.html)
for more information


```{r hub_ens}
# Mean ensemble
round1_ens <- hubEnsembles::simple_ensemble(round1)
head(round1_ens)
```


## Plot

See 
[hubVis package](https://infectious-disease-modeling-hubs.github.io/hubVis/index.html)
for more information

##### Data processing:

Projection:

```{r plot_process}
# Aggregate the data (projection + ensemble)
plot_df <- rbind(round1, round1_ens)
# Add the target_data column for x-axis
plot_df <- dplyr::mutate(plot_df, target_date = as.Date(origin_date) + (horizon * 7) - 1)
```

Truth Data:

```{r truth_data_process}
truth_data <- read.csv("target-data/US_inc_case.csv")
truth_data <- dplyr::filter(truth_data, location == "US", time_idx < min(plot_df$target_date))
```

###### Plot: 

```{r simple_plot, warning=FALSE}
plot_A_inccase <- dplyr::filter(plot_df, scenario_id == "A-2021-03-05", location == "US", target == "inc case")
plot <- hubVis::plot_step_ahead_model_output(plot_A_inccase, truth_data, interactive = FALSE)
plot
```

```{r facet_plot, warning=FALSE}
plot_inccase <- dplyr::filter(plot_df, location == "US", target == "inc case")
plot <- hubVis::plot_step_ahead_model_output(plot_inccase, truth_data, facet = "scenario_id", interactive = FALSE)
plot
```

